---
title: "TAU’ AH"
author: "Lilik Pranowo"
date: "March 22, 2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Alternative code using "dplyr" package:

## Data manipulation

I have checked your code and I when compare with the alternative code that I made using "dplyr" package the results are the same.

load "dplyr" and "tidyr" 

```{r dplyr and tidyr}
library(dplyr)
library(tidyr)
```

Read the data
```{r read data}
dat <- read.csv("ArrestMini.csv")
```

Create new variables: "DATE" and "TIME" from variables "ARRESTTIME" then save it to new dataframe "dat1"
```{r create new variables}
dat1 <- dat %>% 
  separate(ARRESTTIME, c('DATE', 'TIME'), sep = 'T')
```

```{r}
head(dat1)
```

Aggregate council districts that is affected by crime on the day --> I save it as "Arrest_Daily"
```{r}
Arrest_Daily <- dat1 %>%
  mutate(Date = as.Date(DATE, "%m/%d/%Y")) %>%
  group_by(DATE) %>%
  summarize(CASES = n(), NUM_COUNCIL = n_distinct(COUNCIL_DISTRICT)) %>%
  arrange(DATE) 
```

```{r}
Arrest_Daily
```





## Plots

```{r}
rdate <- as.Date(Arrest_Daily$DATE, "%Y-%m-%d")
fix(rdate)
```


```{r plot, echo=FALSE}
plot(Arrest_Daily$NUM_COUNCIL~rdate, type="l", col="red", xlab= "Time", ylab = "Number of council")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
